\documentclass[11pt]{article}
\usepackage{fullpage}
%\usepackage{doublespace}
\begin{document}
\title{Project Proposal}
\author{Optimising the Performances of Proof-of-Work Algorithms on CPU and GPU\\
to Democratise the Cryptocurrency Mining Process \\
\\
Student: Runchao Han (ID: 10140466)\\
Supervisor: Christos Kotselidis \\
}
\maketitle

\section{Background}

Cryptocurrencies like Bitcoin\cite{nakamoto2008bitcoin} implemented through the blockchain technology are at the highest international interest because of their decentralisation and anonymity nature. Proof-of-Work (PoW)\cite{laurie2004proof} based cryptocurrencies rely on computing specific hash values called ``mining'' to get coins, the process of which obtains the consensus on the whole blockchain network\cite{nakamoto2008bitcoin}. However, currently ASIC and FPGA technologies are utilised for mining, making the computing power centralised.

\section{Description}

%This project is to optimise state-of-the-art mining algorithms for better performances on CPU/GPUs, while keeping them memory-consuming and non-parallelisable\cite{back2002hashcash} to minimise the performance gap between CPU/GPU and FGPA/ASIC. Attempts\cite{percival2016scrypt}\cite{dagger}\cite{memohash}\cite{rivest1996time} exist at present, but are proved to be not as successful as expected. This project will take a step further to contribute to the democratisation of cryptocurrencies. 

This project is to optimise state-of-the-art mining algorithms for better performances on CPU/GPUs to minimise the performance gap between CPU/GPU and FGPA/ASIC. Attempts\cite{percival2016scrypt}\cite{dagger}\cite{memohash}\cite{rivest1996time} exist at present, but are proved to be not as successful as expected. This project will take a step further to contribute to the democratisation of cryptocurrencies and better efficiencies of CPU/GPU mining. 

\section{Deliverables}

\begin{enumerate}
\item A thorough review and benchmarking on state-of-the-art mining algorithms.
\item Implementations of optimised mining algorithms and their benchmarking.
\item A brand-new mining algorithm with better performances on CPU/GPU.
\end{enumerate}

\newpage

\bibliographystyle{plain}
\bibliography{proposal.bib}

\end{document}
